`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-16 inst/manuscript/manuscript.rmd
Fix sheet/leaflet terminaology error;

# Introduction
Scramblases are proteins mediating the mass-action driven equilibration of 
lipids between the sheets of lipid bilayers representing biological membranes
<CITE SOME REVIEW>. Indipendent of energy equivalents such as ATP they 
facilitate this ``flipping'' by providing a mechanism of transition through the 
hydrophobic environment of membranes to polar lipid head groups, thus 
reducing the massive energetic cost that process would carry otherwise <CITE 
ANANT HALF TIME>. While the underlying molecular mechanisms remain enigmatic 
<CITE SOMETHING>, and molecules supporting flipping processes as central as the 
equilibration of the ubiquitous phosphoglycerolipids across the membrane of the 
endoplasmic reticulum, where they are synthesized in the cytoplasmic sheet, 
have yet to be identified <CITE SOMETHING>, there has been much recent progress 
in scramblase identification and characterization. Molecules shown to have 
scramblase activity include opsin/rhodopsin <CITE INDU, MIKE, BIRGIT>, X <CITE> 
and Y <CITE>.

>>>>

# Introduction
Scramblases are proteins mediating the mass-action driven equilibration of 
<CITE SOME REVIEW>. Indipendent of energy equivalents such as ATP they 
lipids between the leaflets of lipid bilayers representing biological membranes
facilitate this ``flipping'' by providing a mechanism of transition through the 
hydrophobic environment of membranes to polar lipid head groups, thus 
reducing the massive energetic cost that process would carry otherwise <CITE 
ANANT HALF TIME>. While the underlying molecular mechanisms remain enigmatic 
<CITE SOMETHING>, and molecules supporting flipping processes as central as the 
equilibration of the ubiquitous phosphoglycerolipids across the membrane of the 
endoplasmic reticulum, where they are synthesized in the cytoplasmic leaflet, 
have yet to be identified <CITE SOMETHING>, there has been much recent progress 
in scramblase identification and characterization. Molecules shown to have 
scramblase activity include opsin/rhodopsin <CITE INDU, MIKE, BIRGIT>, X <CITE> 
and Y <CITE>.
